\emph{Cree}: A modern toolbox for readymade economic experiments

### 2015-06-22 Latex/paper.tex
Paper: Alternatives section. Add toolboxes
Added oTree and MWERT. And provided comparisons with MWERT.

\begin{table}[h!]
\begin{tabular}{ l p{0.7\textwidth} }
{\bf Application:} & z-Tree, E-Prime, ESI/ICES Software \\
{\bf Requires Python:} & UAA-PEET \\
{\bf Requires Java:} & BoXS, EconPort, Multistage, Comlab, Aton, JessX, JAuctions, JMarkets, SWIEE \\
{\bf Browser native:} & SoPHIE, Willow, jsPsych, Tatool, QRTEngine, WebExp, WEXTOR, VeconLab \\
\end{tabular}
\end{table}

@@

The fourth category of toolboxes run natively in the web browser, without the need for any browser plug-ins or predownloaded software. These toolboxes place the same low restrictions on the equipment facing subjects as \Cree. However, none of these toolboxes currently support simultaneous real-time interaction between subjects -- ie. it is impossible to design experiments where subjects continuously provide input, while continuously and simultaneously receives feedback from the other subjects. Some toolboxes support sequential decision making, while others completely lack interaction among subjects.

@@

\begin{figure}[h!]
  \caption{Example of a session timeline of a subject}
  \centering
    \includegraphics[width=\textwidth]{figures/example_session}
\end{figure}

>>>>

\begin{table}[h!]
\begin{tabular}{ l p{0.7\textwidth} }
{\bf Application:} & z-Tree, E-Prime, ESI/ICES Software \\
{\bf Requires Python:} & UAA-PEET \\
{\bf Requires Java:} & BoXS, EconPort, Multistage, Comlab, Aton, JessX, JAuctions, JMarkets, SWIEE \\
{\bf Browser native:} & SoPHIE, Willow, jsPsych, Tatool, QRTEngine, WebExp, WEXTOR, VeconLab, oTree, MWERT \\
\end{tabular}
\end{table}

@@

The fourth category of toolboxes run natively in the web browser, without the need for any browser plug-ins or predownloaded software. These toolboxes place the same low restrictions on the equipment facing subjects as \Cree. However, none of these toolboxes, except \emph{MWERT}, currently support simultaneous real-time interaction between subjects -- ie. it is impossible to design experiments where subjects continuously provide input, while they continuously and simultaneously receives feedback from the other subjects. Some toolboxes support sequential decision making, while others completely lack interaction among subjects. The toolbox \emph{MWERT} is build specifically to run real-time multiplayer experiments on the internet \citep{Hawkins_2014}. It relies on many of the same basic technologies as \Cree. However it has been built from scratch to a larger extent than \Cree, which instead relies heavily on existing software libraries. This fore instance imply that researchers will have to rewrite the core of the toolbox to run experiments where more than two subjects interact simultaneously. Whereas the number of subjects is simply a parameter to be specified in \Cree experiments. \emph{MWERT} has a single stage (not considering the stage with instructions and the exit-survey), which can then be repeated a specific number of types. Whereas researchers build a list with stages in \Cree. These stages can be identical but need not be, and in between each stage the researcher can add a synchronisation step or randomisation step, such that subjects wait for other subjects to catch up, or such that subjects are shuffled among groups, roles or treatments.

@@

\begin{figure}[ht!]
  \caption{Example of a session timeline of a subject}
  \centering
    \includegraphics[width=\textwidth]{figures/example_session}
\end{figure}
